Parallel Information Set Generation for Kriegspiel

### 2012-06-28 sbac/paper.tex
Increase font size for figures
Added description of Ranger

\subsubsection{Effect of Load Balancing}
\begin{figure}[h]
\centering
\includegraphics[width=0.7\columnwidth]{plots/3schemes.pdf}
\vspace{-0.1in}
\caption{Effect of load balancing strategy}
\label{3schemes}
\vspace{-0.2in}
\end{figure}

@@

\subsubsection{Effect of Problem Size}
\begin{figure}[h]
\centering
\begin{minipage}{0.5\linewidth}
\includegraphics[width=\columnwidth]{plots/3depths.pdf}
\end{minipage}
\centering
\begin{minipage}{0.5\linewidth}
\includegraphics[width=\columnwidth]{plots/3depthsnolog.pdf}
\end{minipage}
\vspace{-0.1in}
\caption{(Top) Log-log plot of running time for three different sizes of problem as the number of cores used increases.
(Bottom) Same data with a linear y-axis for the running time (to help see the Iso-efficiency.)}
\vspace{-0.2in}
\label{3depths}
\end{figure}

@@

\begin{figure*}[!ht]
\centering
\subfigure[Depth 8]{
\includegraphics[width=2in]{plots/dep8.pdf}
\label{dep8}
} 
\subfigure[Depth 10]{
\includegraphics[width=2in]{plots/dep10.pdf}
\label{dep10}
} 
\subfigure[Depth 12]{
\includegraphics[width=2in]{plots/dep12.pdf}
\label{dep12}
} 
\vspace{-0.1in}
\caption{Grain Size Control for different problem sizes}
%\vspace{-0.1in}
\label{fig:dep}
\vspace{-0.1in}
\end{figure*}

@@

We also evaluated our information set generation routine on 40 positions from actual kriespiel games, including human vs. human and computer vs. computer.  Many of these were trivial to solve in a few seconds or less on a desktop computer.  The running times and speedups for two of the more challenging instances are shown in Tables~\ref{prob4}--\ref{tab:prob5speedups}.  These tables show the results for runs on one to $1024$ cores.  Each column corresponds to a different parameter.  In this case, the grainsize is the number of levels of the search tree that are searched in parallel.  Up to that threshold, each node that is generated spawns a new piece of work, which the {\sc Charm++} runtime schedules to execute on one of the processing elements according to its load balancing strategy.  Above the threshold the entire subtree is searched to completion on a single processor, with no additional parallel overhead.

>>>>

\subsubsection{Effect of Load Balancing}
\begin{figure}[h]
\centering
\includegraphics[width=0.9\columnwidth]{plots/3schemes.pdf}
\vspace{-0.1in}
\caption{Effect of load balancing strategy}
\label{3schemes}
\vspace{-0.2in}
\end{figure}

@@

\subsubsection{Effect of Problem Size}
\begin{figure}[h]
\centering
\begin{minipage}{0.7\linewidth}
\includegraphics[width=\columnwidth]{plots/3depths.pdf}
\end{minipage}
\centering
\begin{minipage}{0.7\linewidth}
\includegraphics[width=\columnwidth]{plots/3depthsnolog.pdf}
\end{minipage}
\vspace{-0.1in}
\caption{(Top) Log-log plot of running time for three different sizes of problem as the number of cores used increases.
(Bottom) Same data with a linear y-axis for the running time (to help see the Iso-efficiency.)}
\vspace{-0.2in}
\label{3depths}
\end{figure}

@@

\begin{figure*}[!ht]
\centering
\subfigure[Depth 8]{
\includegraphics[width=2.2in]{plots/dep8.pdf}
\label{dep8}
} 
\subfigure[Depth 10]{
\includegraphics[width=2.2in]{plots/dep10.pdf}
\label{dep10}
} 
\subfigure[Depth 12]{
\includegraphics[width=2.2in]{plots/dep12.pdf}
\label{dep12}
} 
\vspace{-0.1in}
\caption{Grain Size Control for different problem sizes}
%\vspace{-0.1in}
\label{fig:dep}
\vspace{-0.1in}
\end{figure*}

@@

We also evaluated our information set generation routine on 40 positions from actual kriespiel games, including human vs. human and computer vs. computer.  Many of these were trivial to solve in a few seconds or less on a desktop computer.  For these experiments, we used a real supercomputer - Ranger at TACC~\cite{ranger}. Ranger has 16-way SMP nodes containing AMD Opteron processors. The nodes are interconnected using Infiniband technology in a fully-CLOS topology providing a 1GBps point-to-point bandwidth. The running times and speedups for two of the more challenging instances on Ranger are shown in Tables~\ref{prob4}--\ref{tab:prob5speedups}.   These tables show the results for runs on one to $1024$ cores.  Each column corresponds to a different parameter.  In this case, the grainsize is the number of levels of the search tree that are searched in parallel.  Up to that threshold, each node that is generated spawns a new piece of work, which the {\sc Charm++} runtime schedules to execute on one of the processing elements according to its load balancing strategy.  Above the threshold the entire subtree is searched to completion on a single processor, with no additional parallel overhead.
